### 2013-06-10 paper/jneurosci2013.tex
Second version of the paper, with figures.

%\documentclass[twocolumn]{article}
\documentclass[12pt]{article}
% Change "article" to "report" to get rid of page number on title page
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx,float,wrapfig}
\usepackage{listings}
\usepackage{framed}
\usepackage{inconsolata}
\usepackage{cite}

@@

\newcommand{\framedscalefigone}[3]{
  \begin{figure}[ht!]
    % Requires \usepackage{graphicx}
    \centering
    \begin{framed}
      \begin{minipage}{\textwidth}
        \centering
        \includegraphics[width=#2\columnwidth]{#1}
        \caption{#3}
        \label{#1}
      \end{minipage}
    \end{framed}
  \end{figure}}

\newcommand{\framedscalefigtwo}[4]{
  \begin{figure}[ht!]
    % Requires \usepackage{graphicx}
    \centering
    \begin{framed}
      \begin{minipage}{0.49\textwidth}
        \includegraphics[width=#3\columnwidth]{#1}
      \end{minipage}
      \begin{minipage}{0.49\textwidth}
        \includegraphics[width=#3\columnwidth]{#2}
      \end{minipage}
      \caption{#4}
      \label{#1}
    \end{framed}
  \end{figure}}

@@

\newcommand{\scalefigtwo}[4]{
  \begin{figure}[ht!]
    % Requires \usepackage{graphicx}
    \centering
    \includegraphics[width=#3\columnwidth]{#1}
    \includegraphics[width=#3\columnwidth]{#2}
    \caption{#4}
    \label{#1}
  \end{figure}}

@@

\begin{center} \begin{Large}
  \textbf{A spiking neural circuit model of cortical function
          in simple reaction time tasks}
\end{Large} \end{center}

@@

\begin{abstract}
  todo
\end{abstract}

@@

Animals make complicated motor actions
with high spatial and temporal resolutions.
In temporally precise tasks,
the motor cortex and several afferents coordinate
to bring about motor actions at appropriate times.
For tasks with delay periods,
the medial prefrontal cortex is critically important
for suppressing motor action during the delay period.
This effect has been seen in ?.  %???primates humans rodents etc???.

In rodents, the role of the medial prefrontal cortex
has been investigated through ?.
%???previous work???.
Previously, we have used a simple reaction task
and principal component analysis
to investigate ?. %???summarize Narayana \& laubach jnp 2009???
These results point to neural integration
as playing a key role
in the mPFC's ability
to control the timing of motor actions.

In order to investigate the neural circuit
underlying the production and suppression of motor output,
we extend Singh \& Eliasmith's model to include
neural populations that directly affect the environment,
analogous to the function of Betz cells.
In doing so, we can relate the model to the experimental data
in both neural and behavioural contexts.

\section{Model}

The model presented in this study
is based on a conceptual model of PFC and MC
function in delay tasks proposed by Narayanan and Laubach.
Their conceptual model is based on
principal component analysis of neural data
in rats performing a simple reaction time task.

Figure 1 summarizes their PC analysis.
In PFC, two components account for over 35\%
of variance in population firing.
The first principal component increases slightly
at the time of the lever press,
and then decreases over the delay period.
The second principal component
also increases at the time of lever press,
but remains high until the time of release.

In motor cortex, three components account
for over 60\% of variance in population firing.
The first two principal components are
similar to those found in PFC;
the first steadily decreases over the delay period,
and the second remains high during the delay period.
The third principal component increases
sharply slightly before lever press
and lever release.

The identification of these principal components
leads to a conceptual model of cortical function
during simple reaction time tasks.
This model is summarized in figure 2. % Fig
At the start of a trial,
two complementary systems are activated
to produce quick reactions at the time of a stimulus.
The \textit{prepotent response} system
prepares the motor action that the subject will perform
at the end of the delay period.
The \textit{proactive inhibition} system
suppresses that motor action until the delay period
is over.

\subsection{Neural integration as a core mechanism}

An important observation of Narayanan and Laubach
is that the second principal component
is the cumulative sum (integral)
of the first principal component.
This suggests that some neurons in these cortical areas
are representing the integral of another
signal represented in these areas.

Neural integration through recurrently connected
populations of neurons has been widely studied
in the context of working memory.
% ? cite a bunch -- Mawkinson, Roman, Tanji, X-J Wang, look at singh eliasmith biblio

The Singh and Eliasmith model, in particular,
facilitates a neural implementation of the conceptual model
proposed as a result of the PC analysis.
In addition to outlining a method of constructing
multidimensional neural integrators,
it also provides a method of connecting those integrators
to other populations of neuron representing other signals.

\subsection{Coupled integrators in a control system}

With non-integrative and integrative neuronal populations
as the building blocks, we propose a neural circuit
realization of the conceptual model
discussed in Narayanan and Laubach.
The model is summarized in figure 3.

Two populations are hypothesized to reside in motor cortex.
The \textit{Press/Release} population represents
whether the subject is currently executing
a press or release motor action.
The activity of this population directly affects the environment
in the model, which can be thought of
as functioning like Betz cells.
The \textit{Holding} population tracks
whether or not the subject is currently holding down the lever.
It is analogous to the \textit{prepotent response}
from the conceptual model, as in the absence of inhibition,
it will activate the \textit{Release} neurons
in the \textit{Press/Release} population.
The \textit{Holding} population is integrative,
and integrates the
\textit{Press} signal from the \textit{Press/Release}
population. The integration is controlled
by the \textit{Release} signal, meaning that
when the lever is released the \textit{Holding} signal
is reset to some baseline.

Three populations are hypothesized to reside
in medial prefrontal cortex.
The \textit{Waiting} population represents
that the subject is in a delay state,
waiting for the appropriate time to perform a motor action.
It is analogous to the \textit{proactive inhibition}
from the conceptual model, as it works to balance
the prepotent release response being signaled
from the motor cortex's \textit{Holding} population.
The \textit{Cue} population is sensitive
to the auditory stimulus delivered to the subject
when the delay period is over.
It inhibits the \textit{Waiting} population's
proactive inhibition, disinhibiting \textit{Release}
sensitive neurons.
Similarly, the \textit{Timer} population
tracks the relative amount of time that has passed
since the subject pressed down the lever,
starting the trial.
When the time of the stimulus can be predicted,
the \textit{Timer} population speeds
responding by increasingly inhibiting the
\textit{Waiting} population over time.
It can also effect a motor action on its own by
disinhibiting \textit{Release} neurons sufficiently.
The \textit{Timer} population is integrative,
gradually ramping up as it integrates
the \textit{Waiting} signal.

\section{Methods}

@@

Two models were created to explain neural processing
in the simple reaction time task.
The first is a double-integrator model,
as is described in ?, %???cite singh eliasmith???,
which allows for precise comparisons
between the spiking behaviour of
the model and the empirical subjects
given a controllable behavioural outcome.
The second is an integrated model that
expands the double-integrator model
to include populations that manipulate the environment,
allowing for the comparison between
the model and empirical behaviour.

Both models are made up of heterogeneous populations
of leaky integrate-and-fire neurons
created and connected using the methods
of Eliasmith and Anderson ?. % ???cite???.
Connections between populations of neurons
are determined based on the function computed
through the connection.
Connection weights are determined
by solving a least-squares minimization
of the function representation
given the tuning properties
of the neurons representing the function parameters,
as described in ? %???singheliasmith???
and in detail in ?. %???eliasmith anderson ???.

@@

In  %???cite???
it is shown that
a population of heterogeneous adaptive leaky integrate-and-fire neurons
representing a two-dimensional signal
can capture the dynamics of
working memory cells in prefrontal cortex.
There are, however, several network configurations
that can result in a population of neurons
representing two integrated signals,
as shown in figure ?. %???copy fig 5 from paper???.

We adopt the coupled one-dimensional integrator model,
despite little evidence that reciprocal projections
are localized to smaller integrative populations.
Instead, it is the PCA of mPFC activity
that suggests many neurons are
only sensitive to one of the principal components.
Additionally, it is more intuitive
to connect each principal component with
a separate neural population.
The important task, then,
is to connect each population
with the appropriate value being encoded.

Figure ? %???put in???
summarizes our mapping.
The two coupled one-dimensional oscillators represent
the subject's existence in a particular behavioural state
and how long the subject has been in that state.
The behavioural state is entered
once the subject presses down the lever,
modeled by the activation
of a population of press-sensitive neurons.
The timing integrator is driven
by the state population, as follows from ?. %???citesingh???.
Both coupled integrators are controllable
through a second dimension, %(???cite eliasmith here? ???),
which allows the integrators to be
reset to an initial point (0.0)
when reward is delivered to the subject.
The two one-dimensional integrators
are then projected to an output population that
tracks both signals.

The press- and reward-sensitive populations
drive the rest of the activity of the network.
These two populations are driven by the experimenter,
based on the behaviour being simulated.
For example, for a sequence of correct trials,
the press-sensitive population
will be driven strongly at the start of a trial,
followed 1.6 seconds later
by strongly driving the reward-sensitive population.
For error trials, the reward population
is not driven between activations of the press population.

\subsubsection{Integrated motor-mPFC model}

In order to expand the double-integrator model
to directly manipulate elements of the environment,
three additional variables must be accounted for:
release, auditory cue, and control.

The PCA in ? %???kumar???
revealed
neurons that are sensitive to both press and release.
For this reason, the press-sensitive population
was increased in dimensionality
such that the population was sensitive
to both press and release,
in the same manner to the multidimensional
methods used in ?. %???singh eliasmith???.

The auditory cue ?
%??? todo : see if it's necessary to be an integrator ???

Control is the signal
that causes release-sensitive neurons to fire,
resulting in the release of the lever.
Determining how to implement this control
is one of the primary goals
of mPFC research in tasks with delays.
Its implementation is in itself
a hypothesis of how the mPFC and motor cortex interact
in order to perform these tasks.

\subsubsection{Implementing release control}

? %???kumar???
use their PCA to propose a conceptual model,
shown in Fig ?. %???include???.
We extend this model
by associating prepotent response and proactive inhibition
with neural populations and
showing how they can be connected
such that the model can respond
within the 600 ms response window.

In the double integrator model,
a population of neurons tracks the current behavioural state.
In the integrated model, two populations
track a similar but subtly different quantity.
One population is assumed to exist
in motor cortex, and tracks whether or not
the subject is currently holding down the lever.
This is an integrative population,
which is driven by press-sensitive neurons.
The other population is assumed to exist
in medial PFC, and tracks whether or not
the subject should be delaying the release response.
It is primarily driven by the motor cortex's
holding population.

The motor cortex's holding population
sends excitatory projections
to the release-sensitive neurons,
effecting the prepotent response from the conceptual model.
The medial PFC's waiting population
send inhibitory projects
to the release-sensitive neurons,
effecting the proactive inhibition from the conceptual model.
It should be noted that this organization
produces a slight delay between these two quantities,
with prepotent response occurring first,
quickly followed by proactive inhibition.
This is consistent with ?. %???figure from JNP2009???.

The medial PFC's waiting population's activity
is further modulated by two task-related populations.
One is a ramping population that tracks
the time since the press was initiated.
The other is a cue-sensitive population
that is driven by the onset of the auditory cue.
These two populations
release the proactive inhibition,
causing the release neurons to be disinhibited,
effecting the release of the lever.

As will be discussed further in ?, %???sec???,
the similarity between the two populations
may explain why the first two principal components
of motor cortex and mPFC are very similar.

\subsubsection{Model manipulations}

The model is manipulated in three ways
in this study.

The model emulates the effects of aging
by decreasing the number of neurons
in each neural population,
by uniformly decreasing the strength
of each synapse in the network,
and by randomly removing a fraction
of all synapses in the network.

Lesion studies are emulated
by targeted ablations of either
neurons or synapses in or between specific
neural populations.

Cooling is emulated by
lowering the distribution
of neural gains associated with the
leaky integrate-and-fire neurons
in the neural populations being cooled.
Time constants affecting transmission speed
between populations are raised
to emulate slowed transmission speed
as a result of the cooling of white matter.

@@

Figure 4 summarizes a single trial
of the reaction time task.
In both the empirical and theoretical studies,
the following relevant event times are recorded:
lever press, lever release, reward delivery,
trigger stimulus onset, and house light extinguishing.
Sequences of event times can be used to
identify the result of each trial,
as shown in Figure ?.
Filtering the set of event timestamps
for these sequences identifies each trial outcome.

@@

\section{Results}

\subsection{Model behaviour is less variable}

A stereotypical trial for both the model
and experimental subjects is shown
in Figure 5.
The experimental session lasted ? seconds,
over which ? trials were performed.
? trials were identified as correct trials;
? were premature responses,
and ? were delayed responses.
The model session lasted 500 seconds,
over which ? trials were performed.
? trials were identified as correct trials,
? were premature responses
and ? were delayed responses.

Over all trials for all subjects,
experimental subjects performed ? trials
with a ? \% success rate.
The model performed ? trials with a
? \% success rate.

The distribution of reactions times, shown in figure 5,
is Gaussian-like with a long tail greater than the mean
for both model and data.
The mean reaction time for all experimental subjects
was ? $\pm$ ?.
The mean reaction time for all model subjects
was ? $\pm$ ?.

\subsection{Model principal components are similar}

Principal component analysis on the spike trains
produced by the model show the same number
of primary principal components, with similar shapes.

In the neural populations hypothesized
to reside in motor cortex, as shown in Figure 6,
three leading components are identified.
As in the experimental data,
PC1 is rises around the time of the press
and maintains a high value until the release,
at which point it drops.
PC2, which is very similar
to the cumulative sum of PC1,
is modulated at the time of lever press,
and slowly changes during the delay period.
PC3 is strongly modulated at both the
time of lever press and release.
Firing rates in the model match those in
the data, increasing before the press
and after release.

In the neural populations hypothesized
to reside in medial prefrontal cortex,
as shown in figure 7,
two leading components are identified.
The first component is strongly modulated
around the time of lever press,
and slowly decreases during the delay period.
The second component,
which is similar to the cumulative sum of
PC1, increases at the time of lever press,
and remains high during the delay period.

\subsection{Model manipulations}

Aging results, figure 8.

Lesion results, figure 9.

Cooling results, figure 10.

\subsection{Model behavioural variability is low}

The primary difference is in the amount
of inter-trial and intra-trial variability.
Experimental subjects had several blocks of time
in which they performed as many trials as the model,
but those blocks of time were interrupted by
error trials and time in which the animal
was performing other actions such as grooming.
Within the trial, reaction time distribution
for the model and experimental subjects are
similar but with far less variability.
The model's reactions times
are within the experimental subjects'
mean and standard deviation, however,
suggesting that the model
could have the same variability
by simply injecting noise into the system.
This would also result in
the error trials that are missing in the model.

A better basis for comparison for the model
would be human performance in a similar
reaction time task. ?find some % Look up some behavioural data

\subsection{Model principal components match the data}

While it may be unsurprising
due to the model being inspired by the original
principal component analysis,
it is strong validation for the original conceptual model
that the implemented model maintain
the same principal components
while still being able to simulate behaviours.

? List differences and investigate (with final version of model)

\subsection{Model predictions}

The model manipulations assert that blah has the effect of blah.

Prior studies (some unpublished) have suggested that these are indeed the effects of those things.

Cooling has not been studied in an experimental setting,
and so we take the results as a prediction of the model.

@@

\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{f1-pcasummary}
    \caption{Summary of principal components identified
      by Narayanan and Laubach, 2009. Three components
      were identified in motor cortex (top row), accounting
      for over 60\% of variation.
      Two components were identified in prefrontal cortex
      (bottom row), accounting for over 25\% of variation.}
\end{figure}

@@

\begin{figure}
  \centering
    \includegraphics[width=\columnwidth]{f2-conceptual}
    \caption{The conceptual model proposed by Narayana and
      Laubach, 2009. In the conceptual model, the start of the
      trial activates two systems; one prepares the response
      action (prepotent response) and the other inhibits
      that action until the appropriate time (proactive inhibition).}
\end{figure}

>>>>

\documentclass[12pt]{article}
% Change "article" to "report" to get rid of page number on title page
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx,float,wrapfig}
\usepackage{listings}
\usepackage{framed}
\usepackage{inconsolata}
\usepackage{cite}

@@

@@

@@

\begin{center} \begin{Large}
  \textbf{A task-state model of medial PFC \\ can perform top-down
    control}
\end{Large} \end{center}

@@

\begin{abstract}
  Many hypotheses on the function of medial prefrontal cortex (mPFC)
  have been put forth,
  including action-outcome learning, ???More.
  We adopt a more general approach and posit that
  the mPFC tracks task state,
  which can be usd to accomplish previously hypothesized functions.
  We use as a model rodents performing a simple reaction time (RT) task.
  First, we show that mPFC activity
  tracks task state in the simple RT task,
  and that neural integration is a core mechanism
  for accomplishing task state tracking.
  Second, we show that a working memory model
  using neural integrators closely matches
  rodent neural activity.
  Finally, we propose a neural circuit model
  that imposes top-down control on a control system
  as a proof-of-concept that the task-state model
  can explain the myriad of functions ascribed
  to the medial PFC.
\end{abstract}

@@

mPFC function background

mPFC models background

We propose that the function of the mPFC is to
track task states.
These task states can be very high-dimensional,
if, for example, visual features are necessary
for performing a particular task.
The other functions that have been ascribed
to the mPFC are accomplished
by other areas, but use the task state
information in the mPFC to perform their function.

As an application of this theory,
we investigate a simple reaction-time task.
The remainder of the paper is organized as follows.
First, we review experimental data from rodents
doing the reaction-time task.
The task state space being tracked is determined
by a dimensionality reduction technique
(principal component analysis).
Second, we review a spiking neural model
of working memory and
analyze it during the simple reaction-time task.
Third, we analyze the two-dimensional dynamical system
that makes up the task state space and
show how it changes as a result of performing the task.
Fourth, we create a neural control system
that can perform the simple reaction-time task
and show how the mPFC model can exert top-down control
on that control system.
Finally, we give some examples of how the model
can be manipulated in order to predict
neural and behavioural effects in certain pathologies.

\section{Experimental data}

Narayanan \& Laubach (2009) recorded the medial PFC
of rodents performing a simple reaction-time task
(figure ???).
In this task, the subject presses and holds down the lever
for a delay (the ``foreperiod'';
1 second for the data in this study).
After the foreperiod, an auditory tone (stimulus) is played.
The subject then has 0.6 seconds (the response window)
in which to release the lever.
If the lever is released in that time,
the subject is rewarded.
If the lever is released during the foreperiod,
it is called a premature error,
and is penalized by a time-out.
If the lever is not released within the response window,
it is called a late error,
and is also penalized by a time-out.

Narayanan \& Laubach used principal component analysis
in order to determine the important signals
being represented in the mPFC.
As shown in figure ???,
the first two principal components were significant,
and appear to track
1) if the subject was performing the task, and
2) the relative amount of time the subject has been
performing the task.
Narayanan \& Laubach also found that the neural activity
in the mPFC changed significantly depending on
the outcome of the previous trial;
the first two principal components
change significantly after errors,
and appear to contain a trace that an error occurred.

Interestingly, in the post-correct case,
the first principal components
is very high correlated with the integral
of the second principal components,
and similarly the second principal component
with the integral of the first.
In the post-error case,
these correlations are significantly weaker.
This result suggests that
the mPFC is performing some kind of integration.

\section{Coupled neural integrators}

One model of neural integration is
Singh \& Eliasmith (2006).
Their model was created to explain working memory activity
in PFC during a vibrotactile discrimination task.
It employs two-dimensional neurons in integrative populations
in order to show time-varying activity during the task.
Due to the identification of two strong components
in the rodent data,
we hypothesized that the Singh \& Eliasmith model
could be used to model the simple RT task as well.

There are two different realizations
of this model, as shown in figure ???.
In one, a single population of adaptive
leaky integrate-and-fire neurons tracks both
integrative dimensions, as well as two control dimensions.
In the other, two coupled populations
of adaptive leaky integrate-and-fire neurons
each track one integrative dimension, as well
as one control dimension.
The integrative dimensions are projected
to another population that does not explicitly
represent the control dimensions.
In both realizations of the model,
input to the integrators is provided
by motor actions, and are controlled
by the task outcome.
The idea here is that a motor action
(in this case a lever press)
starts the presistent activations
of one of the integrative dimensions.
That dimension provides input to the other integrative dimension.
Task outcomes (in this case either reward
or time-out penalties) affect the control dimensions,
either stopping all integration
in the reward case or
reversing the integration in the penalty case.

These two different model configurations
make an important distinction between
what is being represented in the brain
area being analyzed.
In our case, should the single population model
match the neural data,
it predicts that the task information
as well as the action and outcome information
is being represented in the mPFC.
If the coupled population model matches
the neural data,
it predicts that only the task information
is being represented, and action and outcome
information only affects the mPFC's
task state.

As can be seen in figure ???,
the coupled integrator model matches
the neural data closely, while the single population model
does not.
In the single population model,
there is highly modulated activity
around the time of reward delivery;
this modulation is not seen in the data.
Therefore, it can be concluded that,
at least for the rodent in a simple RT task,
outcome information is not explicitly
represented in the mPFC,
though the outcome does affect the task
information reflected in mPFC activity.
We will analyze the coupled integrator
realization of the Singh \& Eliasmith
model in the subsequent sections.

\section{Task state space analysis}

If the role of the mPFC is to track the task-state,
then we can view mPFC activity as a trajectory
in the task state space.
This is done in figure ??? for the experimental data,
and the simulated data.

In the post-correct case,
the trajectory through task space is cyclical.
In other words,
when the subject is performing the task properly,
the mPFC travels in a predictable loop.
In the post-error case,
the trajectory through task space is less predictable.

The dynamics of this task state space
can be approximated based on these trajectories,
and on how the Singh \& Eliasmith model was created.
These dynamics are captured in the following equation.

\begin{equation*}
  \begin{bmatrix}
    \dot{x_1} \\ \dot{x_2}
  \end{bmatrix} = \begin{bmatrix}
    -\beta R & 0 \\ \alpha & -\beta R
  \end{bmatrix} \begin{bmatrix}
    x_1 \\ x_2
  \end{bmatrix} + \begin{bmatrix}
    1 & -1 \\ 0 & 0
  \end{bmatrix} \begin{bmatrix}
    A \\ P
  \end{bmatrix} 
\end{equation*}
where $A$ is the action (lever press),
$R$ is the reward, and $P$ is the penalty.
Figure ??? shows the result of directly simulating
the trajectory of this dynamical system.

The Singh \& Eliasmith model uses the methods
of the Neural Engineering Framework (NEF),
which can simulate arbitrary dynamical systems.
The dynamical system defines how the model
encodes information in the populations of neurons,
and how those encoded values are transformed
through connections between populations.
Because we know exactly how the information
is encoded and transformed, we can also
decode that information directly;
this results in figure ???,
which looks like a noisy version
of the mathematical model.
It is important to note that this decoding process
was done on the same neural data that
results in the principal components in figure ???;
therefore, we can say with some certainty
that the mathematical model is closely emulating
the experimental mPFC.

\section{Top-down control of motor actions}

Previous work by Laubach and colleagues (and other groups)
has implicated mPFC as a top-down controller
on the motor cortex in delay tasks like simple RT.
Their work suggests that the mPFC directly inhibits
the motor cortex.
In this paper, we propose instead that the mPFC
can either inhibit, directly excite,
or modulate other activity being projected
to the motor cortex depending on
the part of task-state space the mPFC is in.

In order to demonstrate that this is possible,
we created a simple stimulus-response control system
using the methods used in Singh \& Eliasmith, 2006
(i.e., the NEF; see figure ???).
Briefly, the system is composed of three populations
of adaptive leaky integrate-and-fire neurons.
One population presses and releases the lever,
one population tracks if the lever is currently being held down,
and one population is sensitive to the auditory stimulus,
and stimulates release neurons if the lever
is currently being held down.
This system is trivial to build,
and can perform the simple RT task
with little difficulty (see figure ???).

Top-down control can be accomplished
because of the predictability with which
the mPFC traverses the task state space.
If the subject continues to perform the task correctly,
the release should happen at the same part
of the state space (see figure ???);
if the subject forces a release at the appropriate
part of the state space, it can, in fact,
release the lever faster than it would be able to
if it waits for the stimulus.
In fact, if the foreperiod is completely
predictable, then even devoid of a stimulus,
the subject could perform this task
solely through a forced release mediated
by the mPFC.

Through a similar argument, the mPFC
can also cause the subject to be more
cue-sensitive after errors occur.
When an error occurs, the mPFC is driven to a
low part of the state space.
When the initial press occurs, it may not
be driven to the top part of the state space
as it should; if that occurs (i.e.,
if the subject is performing this task
in the wrong part of the state space),
the subject can attempt to become more cue-sensitive
(see figure ???).

This top-down control can be exerted
on the stimulus-response motor control system
with the network configuration depicted in
figure ???. Briefly, top-down control
is mediated by directly stimulating
the population that is sensitive to the auditory stimulus.
When the mPFC is in the force-release zone,
then these neurons will be excited;
this can either make the population react quicker to
the stimulus, or can directly cause a release
even in the absence of a stimulus.
When the mPFC is in the cue-sensitive zone,
these neurons are stimulated in such a way that
they react quicker and stronger to the stimulus,
but cannot directly cause a release
in the absence of a stimulus.

\section{Task-state space dynamics and errors}

Looking at the dynamics of the task state space
at each part of a simple RT task trial
(figure ???)
gives a full picture of what the task-state
theory of mPFC function predicts is occurring
during the simple RT task.

At the start of a trial,
the system is driven upwards towards [1.0, 0.0].
This sets the initial state for the task.
The subject may have been doing another task
before initiating this RT task;
by resetting to the same initial state,
the subject's behaviour can proceed predictably.
As will be seen, however, after errors,
the system may be sufficiently far from this
initial state that it cannot quite get to the initial state,
and instead operates in an unpredictable part of the task space.

In a correct trial (b), the passive dynamics of the system
push the state to the right
at a predictable (i.e., learned) rate.
The release happens when the state of the system
is sufficiently far to the right (i.e., $x_1$ is high).
If this release happens properly, reward is delivered,
which pushes the system back to the origin.
Then, in the absence of any task-related dynamics,
the system will stay approximately at rest
because the passive dynamics of the system are very weak
at the origin point.

A premature error can be caused by some other factor
(i.e., a motor system mistake) or by the passive dynamics
of the system being too strong in the part of the state space
that the system is driven to once the subject presses the lever.
In the case of some other factor,
the system will receive the negative outcome feedback
before reaching the right side of the state-space,
and be driven to the bottom.
In the case of fast integration,
the system will reach the right side of the state-space,
force a release, and then receive the negative outcome feedback
and be driven to the bottom.
The exact state after receiving the negative feedback
can be used to figure out the cause of the error,
though after some time in the lower part
of the state space, the system will be
driven to the left,
and all that can be decoded
is the notion that an error occurred.

A late error can be caused by either another factor
not responding to the top-down control properly or in time,
by right-ward drift happening too slowly,
or by the system not being driven
to the appropriate place upon pressing down the lever
and drifting slowly as a result.

\section{Behavioural results}

While there are a number of tunable parameters,
(e.g., $\alpha$ and $\beta$ from equation ???),
there are many more parameters that are randomly selected
from probability distributions.
Neuron parameters (neuronal gain, encoding vectors,
adaptation constants, etc.) are all randomized,
and the results of those randomizations are used
to solve for appropriate connection weights.
As such, there is a large amount of variation
between instances of this model.
For that reason,
we generate several instances of the model
and run the model for over forty trials
to get an idea of how
that particular instance of the model behaves.

Figure ??? summarizes the behavioural results
from the experimental rodents, the stimulus-response model
alone, and the stimulus-response model with top-down
control by a coupled integrator model.
The experimental rodents ???.
The stimulus-response model by itself has a relatively slow
reaction time (median ???, $\pm$ ???),
but very high accuracy (??? correct, ??? late, 0\% early).
With top-down control, some models were able to achieve
extremely fast reaction times (e.g., ???).
On average, however, the median reaction time was
??? $\pm$ ???. Note that the variance in reactions times
was much higher with top-down control,
and the accuracy was in general lower (??? correct, ??? late,
??? early).

\section{Model manipulations}

As a spiking neuron model,
this theory of mPFC function is uniquely able to be
manipulated; manipulations at the neural level
can be examined at any point, from the single-cell
to the behavioural level.

One possible manipulation is to
ablate a portion of recurrent synapses,
which could model the effect of brain trauma or aging.
The effects on the mPFC's ability to track the
task state space can be seen in figure ???.
%%% MORE

Since we also know the mathematics behind the mPFC activity,
we can instead manipulate the mathematical model
and make detailed predictions about neural activity.
For example, it is hypothesized that in aging,
recurrent connections become weaker, and therefore
the persistent activity that is seen in working memory models
cannot be maintained for long periods of time.
This can be modeled by including a small damping term, $d < 0$,
in equation ???.

\begin{equation*}
  \begin{bmatrix}
    \dot{x_1} \\ \dot{x_2}
  \end{bmatrix} = \begin{bmatrix}
    -\beta R + d & 0 \\ \alpha & -\beta R + d
  \end{bmatrix} \begin{bmatrix}
    x_1 \\ x_2
  \end{bmatrix} + \begin{bmatrix}
    1 & -1 \\ 0 & 0
  \end{bmatrix} \begin{bmatrix}
    A \\ P
  \end{bmatrix} 
\end{equation*}

In addition to seeing the lower-level effects
of these two manipulations,
we can also make the same manipulations in the full
top-down model. As can be seen in figure ???, % STUFF

\subsection{Predictions}

??? collect together predictions

??? Talk about the results

On interesting feature of the model is its stochastic nature.
While it can be though to represent individual differences,
it is also a useful notion to consider that the model
represents one snapshot during a subject's
learning of the task.
There is no learning in this model;
while the connection weights are solved for ``optimally,''
due to the large amount of noise in the system,
learning would be very likely to fine-tune
the mPFC's ability to traverse and
be sensitive to parts of the task-state space.
Therefore, the poor performance of, for example,
top-down model instance ??? can be thought of as
a subject whose recurrent connection is too strong
and therefore is a poor performer in the task,
or it could be thought of as a subject
who has not yet learned how to properly time
the interval, and after more trials would,
with learning, be able to make less premature errors.

Stepping back, the overarching theory of the paper,
that the mPFC tracks the task state space, ??? more

The theory sets up the possibility for many arbitrary tasks.
Basically, each task has $N$ important dimensions.
The passive dynamics are likely a combination
of integrative and non-integrative dimensions,
enabling for flows in many directions of the space.
The mPFC is drive to specific parts of the state space
based on the sensory environment (e.g.,
being pushed to the top of the state space when lever pressing).
The mPFC then learns to be sensitive to salient
parts of the state space (e.g.,
the force release zone).

\section{Materials and methods}

@@

@@

The Singh \& Eliasmith model (2006).
This model is created using the methods of the
Neural Engineering Framework.
The model uses neural integration in order to explain
neural data in a working memory task.
The paper proposes two candidate models
that can create the desired functional effects
with different neural dynamics.

In the single population model, a single population of
adaptive leaky integrate-and-fire neurons represents
a four-dimensional signal.
A recurrent connection causes the signals
being represented in two of the dimensions
to integrate; the connection
also causes one of the integrative dimensions
to drive the second integrative dimension.
The remaining two dimensions are used
to control the integrative dimensions,
returning them to some baseline activity if necessary.

In the coupled population model, two populations of
adaptive leaky integrate-and-fire neurons represent
two two-dimensional signals.
Recurrent connections on each population cause
one of the represented dimensions to be integrated,
while the other dimension controls the integration.
An explicit connection between one integrative population
drives the integrator in the other population.
Both of the integrative dimensions are then
projected to a final two-dimensional population,
which only represents the integrative signals.

In this paper, we hypothesize that the mPFC
is a realization of one of these two models.
The integrators are driven by the actions taken by the subjects
(e.g., lever pressing),
and are controlled by the outcomes
(e.g., reward delivery).

@@

In both the empirical and theoretical studies,
the following relevant event times are recorded:
lever press, lever release, reward delivery,
trigger stimulus onset, and house light extinguishing.
Sequences of event times can be used to
identify the result of each trial,
as shown in Figure ?.
Filtering the set of event timestamps
for these sequences identifies each trial outcome.

@@

@@

\scalefigone{f1.png}{1.0}{~}

A summary of previous experimental findings. Data from JNP 2009.

A: The simple reaction time task used in the experiment.
The subject presses and holds down the lever
for a delay (also called the foreperiod);
1 second is used in this study.
After the foreperiod, an auditory tone (the stimulus) is played.
The subject then has 0.6 seconds (called the response window)
in which to release the lever.
If the lever is released in that time,
the subject is rewarded with juice.
If the lever is released during the foreperiod,
it is called a premature error,
and is penalized by a 5 second time-out. % NOTE: HOW LONG IS TIMEOUT?
If the lever is not released within the response window,
it is called a late error,
and is also penalized by a 5 second time-out.

B: When lever release events occurred.
Each trial is aligned such that the press event
occurs at time $t=0$.
All of the trials shown are correct trials.
Black dots represent correct trials
that were preceded by correct trials.
Red dots represent correct trials
that were preceded by error trails
(either premature or late).

C: Peri-event spike rasters and histograms
showing different neural activity
based on the previous outcome.
In all six plots, black represents activity
when the last trial was correct, and red
represents activity when the last trial was an error.
The shaded grey areas note where
the neural activity is significantly different
between the two conditions (post-correct and post-error).
In the top row, there is elevated neural activity
before the press is initiated, following an error.
In the middle row, there is elevated neural activity
before the press is initiated (both)
and during the foreperiod (right)
following correct trials.
In the bottom row, there is elevated neural activity
during the whole trial (left)
and after the trial (right)
following error trials.

D: Linear regression with a GLM was performed
on the neural activity.
Before the press is initiated,
18.7\% of neurons encoded the previous outcome,
compared to less than 10\% that
encoded the current reaction time. % WHAT DOES INTERACTION MEAN HERE?

E: Z-statistics showing which neurons were significantly
modulated by the previous outcome, and when.
(Top) Sorted by the absolute value of the Z-statistic.
The bottom 18.7\% of the rows have high average Z-scores
($p > 0.05$?). % WHAT SAYS THOSE ARE SIGNIFICANT?
(Bottom) Sorted by the peak of the Z-statistic.
The line is close to linear, suggesting that the
previous outcome information is being encoded over time
by the entire population. % DOES IT SUGGEST THAT?

@@

\scalefigone{f2.png}{1.0}{~}

A summary of the principal component analysis done
in JNP 2009;
the motivation for investigating Singh \& Eliasmith 2006.

A: A graphical summary of principal component analysis.
Nomarlized peri-event neural data,
in the form of the z-scores of instantaneous firing rates,
is organized in a matrix, with each row
being the z-scored firing rates
of a single neuron on a single trial.
Singular value decomposition is performed on the matrix,
resulting in a matrix such that
the number of columns (time bins) is the same.
The rows are now ordered such that the first row
contains largest eigenvector,
which represents the value when the original
data is projected onto the axes of highest variance.

B: The fraction of variance explained
by each singular value
when PCA is performed on the post-correct neural data
(top), and the post-error data (bottom).
In both cases, the two eigenvectors with the highest
singular values account for nearly 50\% of variance.
The next two eigenvectors also account for an amount
of variance higher than would be expected when
we interpolate from the smaller
singular values.

C: A summary of the loadings of the two top
eigenvector on each neuron.
If a neuron were encoding both the first and second
eigenvectors to the same degree,
we would expect a horizontal line.
The varied lines criss-crossing each other
suggests that each individual neuron
has different sensitivities
to the first and second principal components.

D: The top three principal components
for the post-correct trials (black)
and the post-error trials (red).
